Modelling the Trojan Asteroids

### 2020-04-20 Report/draft1.tex
Further report writing (And changes to planet mass variation)

\input{structure.tex} % Specifies the document structure and loads requires packages
\graphicspath{{"/Users/Kit/OneDrive/Documents/Computing/Trojan Asteroids/Report/Figures"}}
\newcommand*{\subscript}[1]{\ensuremath{_\textrm{{\scriptsize #1}}}}

\usepackage{bm}
\usepackage{tikz}
\usetikzlibrary{calc}

@@

Rescaled solar system units are used for mathematical ease, so distances are measured in astronomical units (AU), time in earth years and mass in multiples of the solar mass.

@@

I also applied the following symmetries:
trojan and greek symmetry (analysis focused on greeks)
rotational symmetry - arbitrary initial point 
direction of orbit
"The combination of these symmetries allows the problem to be simplified. Such that
only the Greeks, orbiting counter-clockwise, with perturbations at t = 0, need to be
investigated.
"

@@

\section{Methodology}
\subsection{Integration Method}
%Put this with theory as "numerical methods"?
%Then all theory could be in methodology?
The default solver is RK45 (an explicit Runge-Kutta method of order 5(4) \cite{Dormand1980}) however this is non-stiff, giving a deviation in asteroid position (from the Lagrange point) in the order of $ 10^{-4}$ AU in the rotating frame over 50 years. This is larger than expected, suggesting the system of equations requires an unreasonable small step size for  numerically stability with respect to this numerical method, even regions where the solution curve is smooth \cite{Lambert1991}. This suggests the system is stiff, and solvers designed for this typically do more work per step, allowing them to take much larger steps, and have improved numerical stability compared to the non-stiff solvers \cite{Byrne1987}.

@@

%Can add more detail on A vs B stability (I believe B stability is relevant here but maybe check this)
\section{Results}
\subsection{Orbit Stability}
\subsection{Wander Analysis}
\subsubsection{Perturbations in z-direction}

@@

>>>>

\input{structure.tex} % Specifies the document structure and loads requires packages
\graphicspath{{"/Users/Kit/OneDrive/Documents/Computing/Trojan Asteroids/Report/Figures"}}

@@

@@

I also applied the following symmetries:
trojan and greek symmetry (analysis focused on greeks)
rotational symmetry - arbitrary initial point 
direction of orbit
"The combination of these symmetries allows the problem to be simplified. Such that
only the Greeks, orbiting counter-clockwise, with perturbations at t = 0, need to be
investigated.
"
(This reduces computing time not hvaing to solve for trojans as well)

@@

\section{Methodology}
This system of coupled first-order differential equations was solved using the scipy solve\_ivp function. The time span was taken as 100 orbits (with 100 points sampled per orbit) unless otherwise stated; this corresponds to 1185 Earth years. Rescaled solar system units are used for mathematical ease, so distances are measured in astronomical units (AU), time in earth years and mass in multiples of the solar mass, and to prevent floating point overflows due to the magnitude of the quantities considered in SI units.

The wander was defined as the maximum distance of the asteroid from the initial point during the orbit (for small perturbations this is also approximately the separation from the Lagrange point).
Initial conditions are defined by the Lagrange point in each frame, with the initial velocity in the stationary frame defined by the period of Jupiter's orbit, and split into Cartesian components.

\subsection{Integration Method}
%Put this with theory as "numerical methods"?
%Then all theory could be in methodology?
Within solve\_ivp, the default solver is RK45 (an explicit Runge-Kutta method of order 5(4) \cite{Dormand1980}) however this is non-stiff, giving a deviation in asteroid position (from the Lagrange point) in the order of $ 10^{-4}$ AU in the rotating frame over 50 years. This is larger than expected, suggesting the system of equations requires an unreasonable small step size for  numerically stability with respect to this numerical method, even regions where the solution curve is smooth \cite{Lambert1991}. This suggests the system is stiff, and solvers designed for this typically do more work per step, allowing them to take much larger steps, and have improved numerical stability compared to the non-stiff solvers \cite{Byrne1987}.

@@

%Can add more detail on A vs B stability (I believe B stability is relevant here but maybe check this)

\subsection{Programme Structure}
Global constants such as solar mass, and sun\textendash planet separation, along with derived values from these such as orbital period and solar radius from centre of mass, as given in an importable python module "\textit{constants}".

Functions to evaluate these coupled differential equation systems are defined in module "\textit{orbits}", while additional functions to evaluate the wander during the orbit (under different sampling routines) are implemented in "\textit{wander}". Further files then import these modules and produce the plots given in this report.

To consider a varying planet mass, it was considered preferable to avoid reconstructing all functions to take this as an argument as this requires re-evaluating all initial derived constants. Therefore, I iterate over alternative masses, re-defining constant values in this instance, and then directly import the required functions to compute the orbit. \textbf{REPHRASE?}

Complete code listings are given in appendix \ref{Code}.

\section{Results}
\subsection{Orbit Stability}
\subsection{Wander Analysis}
\subsubsection{Perturbations in z-direction}

@@

\onecolumn
\begin{appendices}

\section{Code 1} \label{Code}
\begin{lstlisting}[language=Python]
import math
import numpy as np
from scipy import integrate
import matplotlib.pyplot as plt

from constants import G, M_S, M_P, R, ORBIT_NUM, PRECISION  # User defined constants
from constants import (
	solar_rad,
	planet_rad,
	period,
	omega,
	time_span,
)  # Derived constants

\end{lstlisting}
%Can add my own style guide to this, see suggestions on https://www.overleaf.com/learn/latex/code_listing
%\section{Code 2}

\end{appendices}
